An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-15 EconGrowth-R-Functions.Rnw
Updated to-do list on the paper.
CD gamma grid search panels now in correct order. Strip is now transparent. Full country names are included. Unified the "Graph" and "Lattice" versions of the cdeGrid functions. Presentation is now using the lattice version of the function. Eliminated the "Graph" version of the function.

#############################
# This function creates a graph for Cobb-Douglas with energy functions. The graph has 
# a double Y axis. The first Y axis has alpha, beta, and gamma vs. gamma. The second Y axis
# has SSE_y vs. gamma.
# countryAbbrev tells which country you want to view
# energyType tells which type of energy you want
# textScaling tells how you want to scale the text on the axes and other places.
##
cdeGridGraph <- function(countryAbbrev, energyType, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc, textScaling = 1.0){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  # Now melt the data so that it is in the correct form.
  data_molten <- melt(data, id="gamma")
  alphaBetaGammaRange <- c(0.0, 1.0)
  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
  lambdaRange <- c(0.0, 0.004)
  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
  sseRange <- c(0.0, 0.08)
  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08)
  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
  graphType <- "b" #b is for both symbls and lines. Necessary so that the key looks right.
  lineTypes <- c(2, 1, 3, 0) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
  symbols <- c(NA, NA, NA, 1)
  colors <- c("black", "black", "black", "black") #line and symbol colors
  abgGraph <- xyplot(alpha+beta+gamma ~ gamma, data=data,
                     type=graphType,
                     lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
                     pch = symbols, col.symbol = colors, #Controls symbol parameters
                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
                              type=graphType,
                              cex=keyTextSize * textScaling, #controls size of text in the key
                              lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
                              pch=symbols, col=colors, #controls symbol (plot characters) types
                              columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 alternating=FALSE, # eliminates left-right, top-bot alternating of axes
                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
                     ), 
                     ylim=c(0.0, 1.5), #y axis limits
                     #axis labels and scaling
                     xlab=list(label="$\\gamma$", cex=textScaling), 
                     ylab=list(label="$\\alpha$, $\\beta$, $\\gamma$", cex=textScaling)
  )
  sseGraph <- xyplot(SSE ~ gamma, data=data,
                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 y=list(at=c(0.0, 0.02, 0.04, 0.06, 0.08)) #location for y tics                                          
                                 ), 
                     ylim=c(0.0, 0.08),
                     xlab=list(label="$\\gamma$", cex=textScaling), #Not used by the double-Y graph.
                     ylab=list(label="$SSE$", cex=textScaling)
                     )
  # Combine the two graphs into a double-Y graph.
  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)
  return(doubleYGraph)
}

@@

@@

  alphaBetaGammaRange <- c(0.0, 1.0)

@@

  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08, 0.10)

@@

@@

                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics

@@

                     ylim=c(0.0, 1.5), #y axis limits

@@

>>>>

@@

    # Establish some formatting parameters
    stripSpec <- strip.custom(factor.levels=factorLevels, # Sets text for factor levels

@@

    stripSpec <- FALSE # No strip needed.
  alphaBetaGammaRange <- c(-0.1, 1.5)

@@

  sseTics <- c(0.02, 0.04, 0.06, 0.08, 0.10)
  gammaRange <- c(-0.1, 1.1)
  gammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)

@@

                     strip = stripSpec,

@@

                                 x=list(at=gammaTics), #location for x tics
                                 y=list(at=alphaBetaGammaTics)  #location for y tics

@@

                     xlim=gammaRange, #x axis limits
                     ylim=alphaBetaGammaRange, #y axis limits

@@

                     xlim=gammaRange,

### 2013-04-15 EconGrowthSeminar.Rnw
CD gamma grid search panels now in correct order. Strip is now transparent. Full country names are included. Unified the "Graph" and "Lattice" versions of the cdeGrid functions. Presentation is now using the lattice version of the function. Eliminated the "Graph" version of the function.

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("US", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{US}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("UK", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{UK}{0.045}
\end{frame}

>>>>

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
  cdeGridLattice(countryAbbrev="US", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{US}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
  cdeGridLattice(countryAbbrev="UK", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{UK}{0.045}
\end{frame}
